\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
% \usepackage[a4paper, top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textbf{\textit{\small #3}} & \textit{\small #4} \\
    \end{tabular*}\vspace{-9pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}] \setlength{\itemsep}{-7pt}}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeSubHeadingWorkListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingWorkListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-8pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \vspace*{-0.3in}
    {\Huge \scshape Ayuub Mohamud} \\ \vspace{3pt}
    \href{https://www.linkedin.com/in/ayuub-mohamud-405947331/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/ayuub-mohamud-405947331}} ~
    \href{https://github.com/AyuubMohamud}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/AyuubMohamud}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Imperial College London}{Oct 2023 -- Jun 2027}
{MEng Electronic and Information Engineering}{}
\resumeItemListStart
\resumeItem{Currently in 3rd Year}
\resumeItem{\textbf{Modules:} Digital Electronics and Computer Architecture \textbf{(79.78\%)}, Instruction Architectures and Compilers \textbf{(78.74\%)} }
\resumeItemListEnd
\vspace{4mm} %5mm vertical space
\resumeSubheading
{Harris Clapham Sixth Form}{Sep 2021 - Jun 2023}
{A Levels}{}
\resumeItemListStart
\resumeItem{\textbf{Grades: A*AAA }in Mathematics, Further Mathematics, Physics and Computer Science.}
\resumeItemListEnd
\resumeSubHeadingListEnd
%-----------WORK EXPERIENCE-----------
\section{Work Experience}
\resumeSubHeadingWorkListStart
\resumeSubheading
{Arm Holdings plc}{Jun 2025 - Sep 2025}
{Hardware Engineering Intern}{Cambridge}
\resumeItemListStart
\resumeItem{Worked in the little A-core memory system design team.}
\resumeItem{\textbf{Designed} and \textbf{delivered} a testbench infrastructure to \textbf{correlate prefetcher's with software models}.}
\resumeItem{\textbf{Collaborated} with modelling and design teams to understand prefetcher architecture, debug issues, and \textbf{shape training data requirements}.}
\resumeItem{\textbf{Raised and addressed} several issues, \textbf{collaborating} across multiple teams to resolve and improve prefetcher correlation.}
\resumeItemListEnd
\resumeSubheading
{Imperial College London}{Oct 2024 - Mar 2025}
{Undergraduate Teaching Assistant}{Department of Electrical and Electronic Engineering, London}
\resumeItemListStart
\resumeItem{Provided live feedback \textbf{and demonstrations} during programming sessions, helping students grasp modern C++ concepts such as memory management and object-oriented design.}
\resumeItem{Supported first-year students new to programming, strengthening skills in \textbf{abstraction}, \textbf{decomposition}, and problem-solving.}
\resumeItemListEnd
\resumeSubHeadingWorkListEnd

%-----------PROJECTS-----------
\section{Projects}

\resumeSubHeadingListStart

\resumeProjectHeading {\textbf{Out of Order RISC-V Implementation} \href{https://github.com/AyuubMohamud/Biriq}{\scalebox{0.75}\faLink} $|$ SystemVerilog, C++, Hardware} {May 2024 - Apr 2025}
\resumeItemListStart
\resumeItem{Built a 2-way \textbf{configurable, superscalar, speculative, out-of-order} RISC-V CPU.}
\resumeItem{Implemented bimodal \textbf{branch prediction}, bit-manipulation instructions, \textbf{writeback non-blocking cache}.}
\resumeItem{Designed and tested a \textbf{Memory Protection Unit} for address protection using physical addresses. }
\resumeItem{Implemented a \textbf{dedicated test suite} \href{https://github.com/AyuubMohamud/biriqTests}{\scalebox{0.75}\faLink}  in \textbf{make, bash and C++} for finding microarchitectural bugs.}
\resumeItem{Runs on a low-speed grade FPGA at \textbf{82.5MHZ} whilst taking \textbf{around 9K LUTs} and \textbf{4/240} of available DSPs.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Custom mathematical accelerator} \href{https://github.com/AyuubMohamud/MathematicalAccelerator}{\scalebox{0.75}\faLink} $|$ SystemVerilog, C++, Software/Hardware}{May 2025 - Jun 2025}
\resumeItemListStart
\resumeItem{Designed a \textbf{parallel fixed-point accelerator} with \textbf{multi-threaded cores, pipelined arithmetic}, and \textbf{real-time streaming output} for fractal rendering.}
\resumeItem{Implemented a \textbf{custom instruction set, task scheduling}, and \textbf{arbitration logic} to coordinate eight compute cores for \textbf{maximum throughput}.}
\resumeItem{Achieved \textbf{2x} the peak throughput of a single threaded program using \textbf{-O3} on a modern CPU, while consuming \textbf{30000} LUTs, utilising \textbf{Verilator} for \textbf{functional verification} before \textbf{FPGA deployment}.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{TileLink IPs} \href{https://github.com/AyuubMohamud/TileLinkIP}{\scalebox{0.75}\faLink} $|$ SystemVerilog, Hardware} {Nov 2023 - Oct 2024}
\resumeItemListStart
\resumeItem{Built a library of \textbf{configurable reusable IPs}, for building \textbf{embedded SOCs} on FPGAs.}
\resumeItem{Block RAM controllers allow for burst accesses \textbf{maximising} bus bandwidth, including \textbf{atomics}.}
\resumeItem{\textbf{Arbiters, decoders} and N-M connections for \textbf{flexible interconnects} across multiple IPs.}
\resumeItem{\textbf{PLIC} and \textbf{CLINT} controllers for \textbf{interrupt delivery and timer management}, alongside a \textbf{flexible UART controller} for \textbf{external} communication.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{EEERover: 1st Year Engineering Project} $|$ C++, Software/Hardware}{May 2024 - Jun 2024}
\resumeItemListStart
\resumeItem{\textbf{Collaborated} in a team of 6 to develop a rover capable of object detection via multiple sensors.}
\resumeItem{\textbf{Designed} an ultrasound demodulation circuit to decode UART signals.}
\resumeItem{\textbf{Managed} team finances and component sourcing; project awarded a First Class grade.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------SKILLS AND AWARDS-----------
\section{Skills}

\begin{itemize}[leftmargin=0.15in, label={}] 
    \small{\item{
    \textbf{Hardware Description Languages}{: SystemVerilog, Verilog} \\
    \textbf{EDA Tools}{: Synopsys VCS, Synopsys Verdi} \\
    \textbf{Programming Languages}{: C, C++, Python, ARMv8 Assembly, RISC-V Assembly} \\
    \textbf{Protocols}{: TileLink, AXI}
    }}


\end{itemize}

\section{Interests}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Societies}{: Department of Computing Society, Robotics Society, Electrical Engineering Society} \\
      \textbf{Interests}{: Languages, History, Mathematics} \\
    }}
\end{itemize}
\end{document}